---
title: 'tastyfish: a package to develop an index of prey abundance from stomach contents
  data while accounting for predator functional response'
author: "Matthew Robertson"
date: "23/11/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Overview

# Installation

Install the [devtools](https://cran.r-project.org/web/packages/devtools/index.html) package and run:

```{r, eval=FALSE}
devtools::install_github(MatthewRobertson2452\tastyfish)
```

# Example

This example will run through how an index was developed for Northern sand lance using stomach contents data from American plaice. 

For this example, I will be analyzing trawl, full stomach contents, and called stomach contents data. They are all formatted similarly

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("C:\\Users\\mroberts\\OneDrive - Memorial University of Newfoundland\\Marine Institute\\Dissertation Plans\\Chapter 2\\Stomach-Content-Simulation\\New Parameterization")

load("ch2_data.RData")


ampl_call<-subset(ch2_data$spring_call_dat, name=="american plaice")
ampl_full<-subset(ch2_data$spring_sto_dat, Predator_spp_name=="plaice")

spring_camp_surv<-ch2_data$spring_camp_surv

spring_camp_surv<-subset(spring_camp_surv, survey.year!=1995 & survey.year!=2019)

ampl_call<-subset(ampl_call,length>25 & survey.year!=2006 & survey.year!=2016 & survey.year!=2017 & survey.year!=2018 & survey.year!=1995 & survey.year!=2019)
ampl_sto<-subset(ampl_full, Year>2012 & Year!=1995 & Year!=2019)

trawl<-data.frame(year=spring_camp_surv$survey.year, pa=spring_camp_surv$trawl_pa)
call_sto<-data.frame(year=ampl_call$survey.year, pa=ampl_call$pa)
full_sto<-data.frame(year=ampl_sto$Year, pa=ampl_sto$pa)


library(tastyfish)
```

```{r}
head(trawl)
```

We then need to organize all three types of data into one dataframe to develop the data format needed for analyses. This is done by creating a vector that describes the length of each dataset and then inputting the data and that vector (n) into `make_data()`.

```{r}
n<-c(length(trawl$year), length(call_sto$year), length(full_sto$year))

fishy_dat<-make_data(pa=c(trawl$pa, call_sto$pa, full_sto$pa),
          year=c(trawl$year, call_sto$year, full_sto$year),
          n=n)
```

Since both called and full stomach contents data will be treated as having the same functional response we will identify them with the same ID for the model. This ID will be different from the trawl data. The order of the numbers in the `id` vector need to match the order of the dataframes input in `make_data()`.

```{r}
id=c(0,1,1)
```

Now that we have that pre-processing done, we can input that information with some starting values to create the tmb data and parameter lists using `model_data` and `model_param`.

```{r}
tmb_data<-model_data(fishy_dat=fishy_dat, id=id, n=n)

param_list<- model_param(tmb_data, lbeta=log(2), lchi=log(0.5))
```

We can then run the TMB model to calculate the prey index of abundance while also estimating and accouting for the functional response of the predator by using the following code:

```{r, warning=FALSE, message=FALSE, results="hide"}

obj<- TMB::MakeADFun(data = c(model = "matrix_model_new", # which model to use
                                tmb_data),
                       parameters = param_list,
                       DLL = "tastyfish_TMBExports", 
                       random=c("ny")) # package's DLL

opt<-nlminb(obj$par,obj$fn,obj$gr,control = list(trace=10,eval.max=2000,iter.max=1000),silent=TRUE)


rep<-obj$report()
sdrep<-TMB::sdreport(obj)
```

I have also included code to quickly visualize the outputs of the model, for the functional response:

```{r, fig.cap="Estimated functional response for American plaice. Full stomach contents shown as open circles and called stomach contents shown as closed circles."}
plot_curve(rep, tmb_data)
```

And time-series:

```{r, fig.cap="Estimated sand lance index of abundance from models with American plaice stomach contents data. The shaded grey area represents the standard error around the estimated trend. Dashed lines represent the estimated trends from each data source."}
plot_ts(tmb_data, rep, sdrep, unique(spring_camp_surv$year), dat_names=c("Trawl","Called","Full"))
```

